Deciding Bitvector Termination with Program Synthesis

### 2014-07-06 papers/termination/paper.tex
Replace Cristina's (lost) non-determinism stuff

>>>>

\noindent {\bf Non-determinism.} A non-termination diagnosis procedure based on checking the satisfiability of formula {\bf [CNT]}
may fail to find a closed recurrence set for a loop $L=(G, T_u)$ when $T_u$ is non-deterministic.  
To understand the issue, imagine the following loop with an non-deterministic assignment:

\begin{lstlisting}[language=C]
while(x != 0) {
  y = nondet();
  x = x-y;
}
\end{lstlisting}

Only for certain values of \texttt{y} the loop is non-terminating.
In order to restrict the values that may be assigned to \texttt{y}, we need an assumption associated with the non-deterministic choice. 
However, such an assumption may cause a reachable state at the non-deterministic assignment to not have any successor. In such a case
the termination formula would be satisfiable, although the execution halts. This situation can be avoided by checking the existence of 
at least one successor for each reachable state at the non-deterministic assignment. Although we did put a reasonable amount of effort into it, 
we failed to come up with a formulation for the non-termination of such non-deterministic transition relations 
inside the synthesis fragment.
%formula {\bf [Nondet-CNT]} in Definition~\ref{def:nondet-cnt}.
